Evaluation of the NFDI4Objects survey for students and trainees

### 2020-12-15 analysis/paper/paper.Rmd
Datenumformungen

@@

```{r, faecher}

faecher <-  d %>%
  pivot_longer(c(Archaeologie:Restaurierung),
             names_to = "fach",
             values_to = "ja") %>%
  filter(ja == "Ja")

@@

@@

studfach_alle %>%
  filter(Freq > 2) %>%
  ggplot()+
  geom_bar(aes(x = reorder(Var1, Freq), y = Freq), stat = "identity")+
  labs(x = "subjects", 
       y = "frequency (> 2)", 
       name = "Main subject of respondent")+
    coord_flip()

>>>>

# remove "" as input and make NA out of it
# dplyr solution fom here: https://stackoverflow.com/questions/24172111/change-the-blank-cells-to-na

library(dplyr)

empty_as_na <- function(x){
    if("factor" %in% class(x)) x <- as.character(x) ## since ifelse wont work with factors
    ifelse(as.character(x)!="", x, NA)
}

## transform all columns
d <- d %>% 
  mutate_each(funs(empty_as_na))

@@

```{r, faecher_data}

faecher <-  d %>%
  pivot_longer(c(Archaeologie:studienfach.other.),
             names_to = "fach",
             values_to = "ja",
             values_drop_na = FALSE) %>%
  filter(ja != "Nein" &  ja != "N/A")

faecher$fach <- ifelse(faecher$fach == "studienfach.other.", faecher$ja, faecher$fach)

```{r, faecher_textmining_all}

@@

write.csv2(tab_fach, "../data/derived_data/faecheraufstellung.csv", fileEncoding = "UTF-8")

@@

studfach_alle %>%
 # filter(Freq > 2) %>%
  ggplot()+
  geom_bar(aes(x = reorder(Var1, Freq), y = Freq), stat = "identity")+
  labs(x = "subjects", 
     #  y = "frequency (> 2)", 
       name = "Main subject of respondent")+
    coord_flip()

## Bereinigung des Datensatzes

# Liste der Fächer, die wir bei uns sehen:

community <- c("Archaeologie", "Digital Humanities", "Museumswissenschaften", "Anthropologie", "Grabungstechnik", "Architektur.Bauforschung", "Geographie", "Ägyptologie", "Ethnologie", "Restaurierung", "Denkmalpflege", "Archäoinformatik", "wissenschaftliche Ausstellungserarbeitung", "Angewandte Informatik", "Bibliotheks- und Informationwissenschaft",  "Kulturanthropologie", "Klimaforschung", "Numismatik", "Geophysik", "Antike Kulturen Vorderasiens und Ägyptens ", "Antike Kulturen Ägyptens und Vorderasiens ", "Bibliotheksreferendariat", "Prähistorische und Historische Archäologie", "Digitale Denkmaltechnologien (Baufoschung, MINT, Bauingenieurwesen, Heritage,...)", "Altamerikanistik/ Ethnologie", "Altertumswissenschaften", "Ethnologie und Erziehungswissenschaften", "Bibliothekswissenschaft", "Bibliotheksreferendariat mit Master Bibliotheks- und Informationswissenschaft", "Informationswissenschaften", "Informationsmanagement", "Organische Residuenanalysen", )

faecher2 <- subset(faecher, faecher$fach %in% community)
